% Every Latex document starts with a documentclass command
\documentclass[a4paper, 11pt]{article}

% Load some packages
\usepackage{graphicx} % This allows you to put figures in
\usepackage{natbib}   % This allows for relatively pain-free reference lists
\usepackage[left=3cm,top=3cm,right=3cm]{geometry} % The way I like the margins
\usepackage{dsfont}
\usepackage{amsmath}

% This helps with figure placement
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

% Set values so you can have a title
\title{}
\author{}
\date{\today}

% Document starts here
\begin{document}

% Actually put the title in
\maketitle

%\abstract{This is the abstract}

\section{Model assumptions}

\subsection{Conditional prior for the data}
The conditional prior for the data (the photon counts $\{y_i, ..., y_n\}$)
given the parameters\footnote{Conventionally:
the sampling distribution or likelihood.} $\boldsymbol{\theta}$ is Poisson,
where the parameters (including the time delay $\tau$)
determine the Poisson rate for each time bin:
\begin{eqnarray}
p(y_i | \boldsymbol{\theta}) \sim \textnormal{Poisson}
\left(
\lambda_i(\boldsymbol{\theta})
\right).
\end{eqnarray}

At infinite time resolution, the Poisson intensity is a sum of a constant
background level $b$ and $N$ asymmetric biexponential basis functions or
``spikes''. Without any time delay (i.e. if the source were not lensed),
the Poisson intensity would be:

\begin{eqnarray}
\mu_0(t) &=& b + \sum_{i=1}^N f(t; \boldsymbol{\theta}_i)
\end{eqnarray}
where $\boldsymbol{\theta}_i$ is the parameter vector for spike $i$.
With a doubly-imaged system, the non-constant part of the signal appears
again but delayed by $\tau$, the time delay of the system, and scaled by
a constant $C$, the magnification ratio of the two images:
\begin{eqnarray}
\mu(t) &=& b + \sum_{i=1}^N f(t; \boldsymbol{\theta}_i) +
C\sum_{i=1}^N f(t - \tau; \boldsymbol{\theta}_i)
\end{eqnarray}

When observed over a time interval from $t_i - h/2$ to $t_i + h/2$ (where
$h$ is the bin width and $t_i$ the time of the bin centre), the expected
number of photons (given the parameters) is:
\begin{eqnarray}
\lambda_i &=& \int_{t_i - h/2}^{t_i + h/2} \mu(t) \, dt.\label{eq:bin_integral}
\end{eqnarray}

\subsubsection{The Spike Shape}
A spike centered at time $t=t_c$ with amplitude $A$, characteristic timescale
(rise time) $L$ and asymmetry parameter $s$ has the following shape:
\begin{eqnarray}
f(t) &=& \left\{
\begin{array}{lr}
A\exp\left(\frac{t - t_c}{L}\right), & t < t_c\\
A\exp\left(\frac{-(t - t_c)}{sL}\right), & t \geq t_c
\end{array}
\right.
\end{eqnarray}
Therefore the parameter vector of a spike is
$\boldsymbol{\theta}_i = \{A_i, t_c^i, L_i, s_i\}$. One advantage of this
choice of spike shape is that definite integrals (which are needed to compute
the likelihood, because of Equation~\ref{eq:bin_integral} of $f(t)$ are
available analytically.

\subsection{Priors}
The model is parameterised by the following parameters:
\begin{eqnarray}
\left\{
N, \tau, b, \{\boldsymbol{\theta}_i\}_{i=1}^N
\right\}.
\end{eqnarray}
We must specify prior distributions for all of these parameters. Since the
number of spikes $N$ may not be small, we will specify the priors for the
spike parameters hierarchically by introducing hyperparameters
denoted collectively by $\boldsymbol{\alpha}$, of which there will be nine.
We allow $N$ to be any integer from 0 to 100 inclusive, so
the parameter space has 12 -- 412 dimensions. The prior distributions are
specified below.

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|l|l|}
\hline
Parameter			&		Prior\\
\hline
$N$					&		$U(\{0, 1, 2, ..., 100\})$\\
\hline
{\bf Hyperparameters}	&	\\
\hline
$\mu_A$				&		$p(\ln(\mu_A))\sim\textnormal{Cauchy}(0, 1)T(-21.3, 21.3)$\\
$\mu_L$				&		$U(-10, 10)$\\
$\mu_s$				&		$U(-10, 10)$\\
$c_A$				&		$U(-10, 10)$\\
$c_L$				&		$U(-10, 10)$\\
$c_s$				&		$U(-10, 10)$\\
$\sigma_A$			&		$p\left(\ln(\sigma_A)\right) \sim \mathcal{N}(0, 1)$\\
$\sigma_L$			&		$p\left(\ln(\sigma_L)\right) \sim \mathcal{N}(0, 1)$\\
$\sigma_s$			&		$p\left(\ln(\sigma_s)\right) \sim \mathcal{N}(0, 1)$\\
\hline
{\bf Spike parameters}	&	\\
\hline
$A_i$				&	$p(\ln(A_i))\sim\mathcal{N}\left(\right)$\\
$L_i$				&		\\
$s_i$				&	\\
$t_c^i$				&	\\
\end{tabular}
\end{center}
\end{table}

\section*{Acknowledgements}
Our model is very closely related to the one used in Daniela Huppenkothen's
{\it Magnetron} and {\it magnetronhierarchy} projects \citep{magnetron}: so
much so that we should consider making her and Iain Murray coauthors.
This work was supported by a Marsden Fast Start grant from the Royal Society of
New Zealand.

\begin{thebibliography}{}
\bibitem[Huppenkothen et al.(2015)]{magnetron} Huppenkothen, D., 
Brewer, B.~J., Hogg, D.~W., Murray, I., Frean, M., Elenbaas, C., Watts, 
A.~L., Levin, Y., van der Horst, A.~J., Kouveliotou, C.\ 2015.\ Dissecting 
magnetar variability with Bayesian hierarchical models.\ ArXiv e-prints 
arXiv:1501.05251.
\end{thebibliography}


\end{document}

